Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-10-25 paper.tex
Clean up some more text already edited

We integrate these equations through the simulated spacetime
over which the following volume data are known
(all defined in App.~\ref{sec:definitions}):
the spacetime metric $\psi_{\alpha\beta}$,
its derivatives $\psi_{\alpha\beta,\gamma}$,
the fluid velocity $u_i$,
Lorentz factor $W$,
density $\varrho$,
temperature $T$,
and electron fraction $Y_e$.
These fields are stored in spectral representation.
If they are computed via hydrodynamical simulation, they are saved to disk
at specified coordinate times and interpolated
with spectral interpolation in space,
and 1st-order polynomial interpolation in time
(as described in \cite[App.~B]{bohn2016-code}).
If computed from a quasi-stationary solution to the
\footnote{TODO: clarify quasistationary timescale}
general relativistic hydrodynamics equations,
a single time is stored to disk, and no time interpolation is needed.

@@

\subsection{Infinite Homogeneous Moving Slab:
  Testing Doppler Shift}
\label{ssec:test_doppler}
We reproduce the test above (again in Minkowski spacetime),
but with the matter and observer in relative motion.
We use a stationary observer
and fluid moving in the positive $z$-direction:
with $u^\alpha \rightarrow W(1,0,0,v)$ and $W=(1-v^2)^{-1/2}$.
All other thermodynamic variables and background fields are unchanged
since our ray integration uses these quantities in the fluid frame.

@@

In addition to the fluid velocity and Lorentz factor, described above, the
other fluid state variables we use from our hydrodynamic simulations
are rest density $\varrho=m_b n_b$, temperature $T$, and electron fraction
\begin{equation}
  Y_e = \frac{n_{e^-} - n_{e^+}}{n_b},
\end{equation}
with $n_{e^-}$, $n_{e^+}$, and $n_b$, the number densities of electrons
positrons, and baryons, and $m_b$ is the average baryon mass.

>>>>

We integrate these equations through the simulated spacetime
over which the following volume data are known:
the spacetime metric $\psi_{\alpha\beta}$,
its derivatives $\psi_{\alpha\beta,\gamma}$,
the fluid velocity $u_i$,
Lorentz factor $W$,
density $\varrho$,
temperature $T$,
and electron fraction $Y_e$,
all defined in App.~\ref{sec:definitions}.
These fields are stored in spectral representation.
If they are computed via hydrodynamical simulation, they may be saved to disk
at specified coordinate times and interpolated
with spectral interpolation in space,
and 1st-order polynomial interpolation in time
(as described in \cite[App.~B]{bohn2016-code}).
If computed from a quasi-stationary solution to the
general relativistic hydrodynamics equations,
a single time is stored to disk, and no time interpolation is needed.
In this paper for simplicity and to limit computational memory loads,
we limit ourselves to quasistationary configurations
and use single time slices in every test case.

@@

\subsection{Infinite Homogeneous Moving Slab:
  Testing Doppler Shift}
\label{ssec:test_doppler}
We reproduce the test above, again in Minkowski spacetime,
but with the matter and observer in relative motion.
We use a stationary observer
and fluid moving in the positive $z$-direction:
with $u^\alpha \rightarrow W(1,0,0,v)$ and $W=(1-v^2)^{-1/2}$,
where $W$ is the Lorentz factor defined in App.~\ref{sec:definitions}.
All other thermodynamic variables and background fields are unchanged
since our ray integration uses these quantities in the fluid frame.

@@

In addition to the fluid velocity and Lorentz factor, described above, the
other fluid state variables we use from our hydrodynamic simulations
are rest density $\varrho=m_b n_b$, temperature $T$, and electron fraction
\begin{equation}
  Y_e = \frac{n_{e^-} - n_{e^+}}{n_b},
\end{equation}
where $n_{e^-}$, $n_{e^+}$, and $n_b$ are the number densities of electrons
positrons, and baryons, and $m_b$ is the average baryon mass.
